---
title: "Thesis data collection"
output: html_document
date: "2023-07-02"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown contains the data and code used in my thesis for the MSc Applied Social Data Science at the LSE. The title of the paper is as follows: Decrypting Political Discourse: A comparative exploration of inequality in the Budget statements of the Labour Party (1997-2010) and the Conservative Party (2010-current).

 
This study takes a three-fold approach to answer the research question: 
1.	How are inequalities discussed in the Budget statements of the Conservative and Labour parties? 
2.	How are inequalities represented in the Budget statements of the Conservative and Labour parties? 

```{r}
library(rvest)
library(httr)
library(tidyverse)
library("udpipe")
library(quanteda)
library(quanteda.textplots)
library(quanteda.textstats)
library(quanteda.dictionaries)
library(tidytext)

## Begin with Conservative Party speeches 


url <- "https://www.gov.uk/government/speeches/spring-budget-2023-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 338:1098)

budget23 <- data.frame(paste(content$c............Spring.Budget.2023.speech...GOV.UK................., collapse = ""))

year <- c(2023)
budget23$year <- year

budget23 <- budget23 %>% rename(text = paste.content.c............Spring.Budget.2023.speech...GOV.UK...................)

# 2022 November
url <- "https://www.gov.uk/government/speeches/the-autumn-statement-2022-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 345:1013)

budget22 <- data.frame(paste(content$c............The.Autumn.Statement.2022.speech...GOV.UK........., collapse = ""))

year <- c(2022)
budget22$year <- year

budget22 <- budget22 %>% rename(text = paste.content.c............The.Autumn.Statement.2022.speech...GOV.UK...........)

# 2021 August 
url <- "https://www.gov.uk/government/speeches/autumn-budget-and-spending-review-2021-speech"
response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 346:1667)

budget21b <- data.frame(paste(content$c............Autumn.Budget.and.Spending.Review.2021.Speech...GOV.UK..., collapse = ""))

year <- c(20212)
budget21b$year <- year

budget21b <- budget21b %>% rename(text = paste.content.c............Autumn.Budget.and.Spending.Review.2021.Speech...GOV.UK.....)


# 2021 March 
url <- "https://www.gov.uk/government/speeches/budget-speech-2021"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 341:1124)

budget21a <- data.frame(paste(content$c............Budget.Speech.2021...GOV.UK.......................CDATA...., collapse = ""))

year <- c(2021)
budget21a$year <- year

budget21a <- budget21a %>% rename(text = paste.content.c............Budget.Speech.2021...GOV.UK.......................CDATA......)

# 2020 March
url <- "https://www.gov.uk/government/speeches/budget-speech-2020"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 

content <- as.data.frame(content)
content <- slice(content, 341:1616)

budget20 <- data.frame(paste(content$c............Budget.Speech.2020...GOV.UK.......................CDATA...., collapse = ""))

year <- c(2020)
budget20$year <- year

budget20 <- budget20 %>% rename(text = paste.content.c............Budget.Speech.2020...GOV.UK.......................CDATA......)

# No budget in 2019! 

# 2018

url <- "https://www.gov.uk/government/speeches/budget-2018-philip-hammonds-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 338:1762)

budget18 <- data.frame(paste(content$c............Budget.2018..Philip.Hammond.s.speech...GOV.UK..., collapse = ""))

year <- c(2018)
budget18$year <- year

budget18 <- budget18 %>% rename(text = paste.content.c............Budget.2018..Philip.Hammond.s.speech...GOV.UK.....)

# 2017 November 

url <- "https://www.gov.uk/government/speeches/autumn-budget-2017-philip-hammonds-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 346:1452)

budget17b <- data.frame(paste(content$c............Autumn.Budget.2017..Philip.Hammond.s.speech...GOV.UK..., collapse = ""))

year <- c(20172)
budget17b$year <- year

budget17b <- budget17b %>% rename(text = paste.content.c............Autumn.Budget.2017..Philip.Hammond.s.speech...GOV.UK.....)

# 2017 March 

url <- "https://www.gov.uk/government/speeches/spring-budget-2017-philip-hammonds-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 343:943)

budget17a <- data.frame(paste(content$c............Spring.Statement.2017..Philip.Hammond.s.speech...GOV.UK..., collapse = ""))

year <- c(2017)
budget17a$year <- year

budget17a <- budget17a %>% rename(text = paste.content.c............Spring.Statement.2017..Philip.Hammond.s.speech...GOV.UK.....)

# 2016 March
url <- "https://www.gov.uk/government/speeches/budget-2016-george-osbornes-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 343:1458)

budget16 <- data.frame(paste(content$c............Budget.2016..George.Osborne.s.speech...GOV.UK..., collapse = ""))

year <- c(2016)
budget16$year <- year

budget16 <- budget16 %>% rename(text = paste.content.c............Budget.2016..George.Osborne.s.speech...GOV.UK.....)

# 2015 July 
url <- "https://www.gov.uk/government/speeches/chancellor-george-osbornes-summer-budget-2015-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 343:1366)

budget15b <- data.frame(paste(content$c............Chancellor.George.Osborne.s.Summer.Budget.2015.speech...GOV.UK..., collapse = ""))

year <- c(2015)
budget15b$year <- year

budget15b <- budget15b %>% rename(text = paste.content.c............Chancellor.George.Osborne.s.Summer.Budget.2015.speech...GOV.UK.....)

# 2015 March
url <- "https://www.gov.uk/government/speeches/chancellor-george-osbornes-budget-2015-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 348:1314)

budget15a <- data.frame(paste(content$c............Chancellor.George.Osborne.s.Budget.2015.speech...GOV.UK..., collapse = ""))

year <- c(2015)
budget15a$year <- year

budget15a <- budget15a %>% rename(text = paste.content.c............Chancellor.George.Osborne.s.Budget.2015.speech...GOV.UK.....)


# 2014 March
url <- "https://www.gov.uk/government/speeches/chancellor-george-osbornes-budget-2014-speech"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 

content <- as.data.frame(content)
content <- slice(content, 360:1309)

budget14 <- data.frame(paste(content$c............Chancellor.George.Osborne.s.Budget.2014.speech...GOV.UK..., collapse = ""))

year <- c(2014)
budget14$year <- year

budget14 <- budget14 %>% rename(text = paste.content.c............Chancellor.George.Osborne.s.Budget.2014.speech...GOV.UK.....)

# 2013 March
url <- "https://www.gov.uk/government/speeches/budget-2013-chancellors-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 

content <- as.data.frame(content)
content <- slice(content, 353:1248)

budget13 <- data.frame(paste(content$c............Budget.2013..Chancellor.s.statement...GOV.UK..., collapse = ""))

year <- c(2013)
budget13$year <- year

budget13 <- budget13 %>% rename(text = paste.content.c............Budget.2013..Chancellor.s.statement...GOV.UK.....)


#2012 March
url <- "https://www.gov.uk/government/speeches/autumn-statement-2012-chancellors-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 353:1084)

budget12 <- data.frame(paste(content$c............Autumn.Statement.2012..Chancellor.s.statement...GOV.UK..., collapse = ""))

year <- c(2012)
budget12$year <- year

budget12 <- budget12 %>% rename(text = paste.content.c............Autumn.Statement.2012..Chancellor.s.statement...GOV.UK.....)


#2011 March
url <- "https://publications.parliament.uk/pa/cm201011/cmhansrd/cm110323/debtext/110323-0001.htm#11032368001031"
content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 572:967)


budget11 <- data.frame(paste(content$df, collapse = ""))

year <- c(2011)
budget11$year <- year
budget11 <- budget11 %>% rename(text = paste.content.df..collapse......)


#2010 June
# "https://hansard.parliament.uk/commons/2010-06-22/debates/10062245000001/FinancialStatement"

budget10 <- readLines("~/Documents/ASDS/Quant/Financial Statement 2010-06-22.txt", encoding = "UTF-8")

budget10 <- as.data.frame(budget10)

budget10$budget10 <- gsub("\\d{2}:\\d{2}:\\d{2}", "", budget10$budget10)

budget10 <- budget10[3:nrow(budget10), ]
budget10 <- as.data.frame(budget10)

budget10 <- data.frame(paste(budget10$budget10, collapse = ""))

year <- c(2010)
budget10$year <- year

budget10 <- budget10 %>% rename(text = paste.budget10.budget10..collapse......)



################################################################################
# Now the Labour Party


## June 1997
url <- "https://api.parliament.uk/historic-hansard/commons/1997/jul/02/budget-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 68:203)

budget97 <- data.frame(paste(content$c..Budget.Statement..Hansard..2.July.1997.......var.appInsights.window.appInsights..function.a....., collapse = ""))

year <- c(1997)
budget97$year <- year

budget97 <- budget97 %>% rename(text = paste.content.c..Budget.Statement..Hansard..2.July.1997.......var.appInsights.window.appInsights..function.a.......)


## March 1998 - each part of the bill is split up so have to do it separately. 
url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/introduction"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 57:63)

budget98 <- data.frame(paste(content$c..INTRODUCTION..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98a <- budget98 %>% rename(text = paste.content.c..INTRODUCTION..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/stability-and-prudence"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:131)

budget98 <- data.frame(paste(content$c..STABILITY.AND.PRUDENCE..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98b <- budget98 %>% rename(text = paste.content.c..STABILITY.AND.PRUDENCE..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/enterprise"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:166)

budget98 <- data.frame(paste(content$c..ENTERPRISE..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98c <- budget98 %>% rename(text = paste.content.c..ENTERPRISE..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/work"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:251)

budget98 <- data.frame(paste(content$c..WORK..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98d <- budget98 %>% rename(text = paste.content.c..WORK..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)


url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/supporting-families-and-children"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:192)

budget98 <- data.frame(paste(content$c..SUPPORTING.FAMILIES.AND.CHILDREN..Hansard..17.March.1998...., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98e <- budget98 %>% rename(text = paste.content.c..SUPPORTING.FAMILIES.AND.CHILDREN..Hansard..17.March.1998......)

url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/section-7-other-tax-measures"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:94)

budget98 <- data.frame(paste(content$c..SECTION.7..OTHER.TAX.MEASURES..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98f <- budget98 %>% rename(text = paste.content.c..SECTION.7..OTHER.TAX.MEASURES..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)


url <- "https://api.parliament.uk/historic-hansard/commons/1998/mar/17/public-spending"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:78)

budget98 <- data.frame(paste(content$c..PUBLIC.SPENDING..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1998)
budget98$year <- year

budget98g <- budget98 %>% rename(text = paste.content.c..PUBLIC.SPENDING..Hansard..17.March.1998.......var.appInsights.window.appInsights..function.a.......)

budget98 <- budget98a %>%
  full_join(budget98b, by = c("text", "year")) %>%
    full_join(budget98c, by = c("text", "year")) %>%
      full_join(budget98d, by = c("text", "year")) %>%
    full_join(budget98e, by = c("text", "year")) %>%
    full_join(budget98f, by = c("text", "year")) %>%
    full_join(budget98g, by = c("text", "year"))


budget98 <- data.frame(paste(budget98$text, collapse = ""))

budget98 <- budget98 %>% rename(text = paste.budget98.text..collapse......)

year <- c(1998)
budget98$year <- year
## 1999
url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/introduction"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 57:70)

budget99 <- data.frame(paste(content$c..INTRODUCTION..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99a <- budget99 %>% rename(text = paste.content.c..INTRODUCTION..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/stability"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:231)

budget99 <- data.frame(paste(content$c..STABILITY..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99b <- budget99 %>% rename(text = paste.content.c..STABILITY..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/enterprise"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:353)

budget99 <- data.frame(paste(content$c..ENTERPRISE..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99c <- budget99 %>% rename(text = paste.content.c..ENTERPRISE..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/environment"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:116)

budget99 <- data.frame(paste(content$c..ENVIRONMENT..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99d <- budget99 %>% rename(text = paste.content.c..ENVIRONMENT..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)


url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/families"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:225)

budget99 <- data.frame(paste(content$c..FAMILIES..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99e <- budget99 %>% rename(text = paste.content.c..FAMILIES..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/the-elderly"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:211)

budget99 <- data.frame(paste(content$c..THE.ELDERLY..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99f <- budget99 %>% rename(text = paste.content.c..THE.ELDERLY..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)


url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/work"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:235)

budget99 <- data.frame(paste(content$c..WORK..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99g <- budget99 %>% rename(text = paste.content.c..WORK..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

url <- "https://api.parliament.uk/historic-hansard/commons/1999/mar/09/modernising-public-services"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 51:183)

budget99 <- data.frame(paste(content$c..MODERNISING.PUBLIC.SERVICES..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(1999)
budget99$year <- year

budget99h <- budget99 %>% rename(text = paste.content.c..MODERNISING.PUBLIC.SERVICES..Hansard..9.March.1999.......var.appInsights.window.appInsights..function.a.......)

budget99 <- budget99a %>%
  full_join(budget99b, by = c("text", "year")) %>%
    full_join(budget99c, by = c("text", "year")) %>%
    full_join(budget99d, by = c("text", "year")) %>%
    full_join(budget99e, by = c("text", "year")) %>%
    full_join(budget99f, by = c("text", "year")) %>%
    full_join(budget99g, by = c("text", "year")) %>%
    full_join(budget99h, by = c("text", "year"))


budget99 <- data.frame(paste(budget99$text, collapse = ""))

budget99 <- budget99 %>% rename(text = paste.budget99.text..collapse......)
year <- c(1999)
budget99$year <- year

## 2000
url <- "https://api.parliament.uk/historic-hansard/commons/2000/mar/21/budget-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 68:300)

budget00 <- data.frame(paste(content$c..Budget.Statement..Hansard..21.March.2000.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(2000)
budget00$year <- year

budget00 <- budget00 %>% rename(text = paste.content.c..Budget.Statement..Hansard..21.March.2000.......var.appInsights.window.appInsights..function.a.......)


## 2001
url <- "https://api.parliament.uk/historic-hansard/commons/2001/mar/07/budget-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 68:216)

budget01 <- data.frame(paste(content$c..Budget.Statement..Hansard..7.March.2001.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(2001)
budget01$year <- year

budget01 <- budget01 %>% rename(text = paste.content.c..Budget.Statement..Hansard..7.March.2001.......var.appInsights.window.appInsights..function.a.......)

## 2002
url <- "https://api.parliament.uk/historic-hansard/commons/2002/apr/17/budget-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 68:242)

budget02 <- data.frame(paste(content$c..Budget.Statement..Hansard..17.April.2002.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(2002)
budget02$year <- year

budget02 <- budget02 %>% rename(text = paste.content.c..Budget.Statement..Hansard..17.April.2002.......var.appInsights.window.appInsights..function.a.......)


## 2003
url <- "https://api.parliament.uk/historic-hansard/commons/2003/apr/09/budget-statement"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 68:249)

budget03 <- data.frame(paste(content$c..Budget.Statement..Hansard..9.April.2003.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(2003)
budget03$year <- year

budget03 <- budget03 %>% rename(text = paste.content.c..Budget.Statement..Hansard..9.April.2003.......var.appInsights.window.appInsights..function.a.......)


## 2004
url <- "https://api.parliament.uk/historic-hansard/commons/2004/mar/17/introduction"

response <- GET(url)

content <- read_html(response) %>% html_text()

content <- content %>%
  strsplit(split = "\n") 


content <- as.data.frame(content)
content <- slice(content, 55:225)

budget04 <- data.frame(paste(content$c..INTRODUCTION..Hansard..17.March.2004.......var.appInsights.window.appInsights..function.a....., collapse = ""))


year <- c(2004)
budget04$year <- year

budget04 <- budget04 %>% rename(text = paste.content.c..INTRODUCTION..Hansard..17.March.2004.......var.appInsights.window.appInsights..function.a.......)

## 2005
url <- "https://publications.parliament.uk/pa/cm200405/cmhansrd/vo050316/debtext/50316-04.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 12:322)

budget05 <- data.frame(paste(content$df, collapse = ""))

year <- c(2005)
budget05$year <- year

budget05 <- budget05 %>% rename(text = paste.content.df..collapse......)

## 2006
url <- "https://publications.parliament.uk/pa/cm200506/cmhansrd/vo060322/debtext/60322-05.htm#60322-05_head2"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 13:397)

budget06 <- data.frame(paste(content$df, collapse = ""))

year <- c(2006)
budget06$year <- year

budget06 <- budget06 %>% rename(text = paste.content.df..collapse......)

## 2007 
url <- "https://publications.parliament.uk/pa/cm200607/cmhansrd/cm070321/debtext/70321-0004.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 10:162)

budget07a <- data.frame(paste(content$df, collapse = ""))


budget07a <- budget07a %>% rename(text = paste.content.df..collapse......)
url <- "https://publications.parliament.uk/pa/cm200607/cmhansrd/cm070321/debtext/70321-0005.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 5:148)

budget07b <- data.frame(paste(content$df, collapse = ""))

budget07b <- budget07b %>% rename(text = paste.content.df..collapse......)

budget07 <- budget07a %>%
  full_join(budget07b, by = c("text"))

budget07 <- data.frame(paste(budget07$text, collapse = ""))

budget07 <- budget07 %>% rename(text = paste.budget07.text..collapse......)

year <- c(2007)
budget07$year <- year

## 2008 

url <- "https://publications.parliament.uk/pa/cm200708/cmhansrd/cm080312/debtext/80312-0004.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 7:168)

budget08a <- data.frame(paste(content$df, collapse = ""))

year <- c(2008)
budget08a$year <- year

budget08a <- budget08a %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200708/cmhansrd/cm080312/debtext/80312-0005.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 6:163)

budget08b <- data.frame(paste(content$df, collapse = ""))

year <- c(2008)
budget08b$year <- year

budget08b <- budget08b %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200708/cmhansrd/cm080312/debtext/80312-0006.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 6:54)

budget08c <- data.frame(paste(content$df, collapse = ""))

year <- c(2008)
budget08c$year <- year

budget08c <- budget08c %>% rename(text = paste.content.df..collapse......)


budget08 <- budget08a %>%
  full_join(budget08b, by = c("text", "year")) %>%
  full_join(budget08c, by = c("text", "year")) 

budget08 <- data.frame(paste(budget08$text, collapse = ""))

budget08 <- budget08 %>% rename(text = paste.budget08.text..collapse......)

year <- c(2008)
budget08$year <- year

## 2009 

url <- "https://publications.parliament.uk/pa/cm200809/cmhansrd/cm090422/debtext/90422-0003.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 184:202)

budget09a <- data.frame(paste(content$df, collapse = ""))

year <- c(2009)
budget09a$year <- year

budget09a <- budget09a %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200809/cmhansrd/cm090422/debtext/90422-0004.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 5:223)

budget09b <- data.frame(paste(content$df, collapse = ""))

year <- c(2009)
budget09b$year <- year

budget09b <- budget09b %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200809/cmhansrd/cm090422/debtext/90422-0005.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 5:155)

budget09c <- data.frame(paste(content$df, collapse = ""))


budget09c <- budget09c %>% rename(text = paste.content.df..collapse......)


budget09 <- budget09a %>%
  full_join(budget09b, by = c("text")) %>%
  full_join(budget09c, by = c("text")) 

budget09 <- data.frame(paste(budget09$text, collapse = ""))

budget09 <- budget09 %>% rename(text = paste.budget09.text..collapse......)
year <- c(2009)
budget09$year <- year

## 2010
url <- "https://publications.parliament.uk/pa/cm200910/cmhansrd/cm100324/debtext/100324-0004.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 23:197)

budget10a <- data.frame(paste(content$df, collapse = ""))

year <- c(2010)
budget10a$year <- year

budget10a <- budget10a %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200910/cmhansrd/cm100324/debtext/100324-0005.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 5:193)

budget10b <- data.frame(paste(content$df, collapse = ""))

year <- c(2010)
budget10b$year <- year

budget10b <- budget10b %>% rename(text = paste.content.df..collapse......)

url <- "https://publications.parliament.uk/pa/cm200910/cmhansrd/cm100324/debtext/100324-0006.htm"

content <- read_html(url) %>% html_text()
content <- gsub("\\s+", " ", content)

# Tokenize the text into sentences using the `udpipe` package
doc <- udpipe(content, object = "english")

df <- doc$sentence

df <- as.data.frame(df)

# Remove repeated sentences
df <- distinct(df)

content <- slice(df, 6:79)

budget10c <- data.frame(paste(content$df, collapse = ""))

year <- c(2010)
budget10c$year <- year

budget10c <- budget10c %>% rename(text = paste.content.df..collapse......)


budget10Lab <- budget10a %>%
  full_join(budget10b, by = c("text", "year")) %>%
  full_join(budget10c, by = c("text", "year")) 

budget10Lab <- data.frame(paste(budget10Lab$text, collapse = ""))
budget10Lab$paste.budget10Lab.text..collapse......

budget10Lab <- budget10Lab %>% rename(text = paste.budget10Lab.text..collapse......)

year <- c(2010)
budget10Lab$year <- year


```

Now make into corpus/dfm data to complete analysis!
```{r}
# Join budgets
c <- budget97 %>%
  full_join(budget98, by = c("year", "text")) %>%
  full_join(budget99, by = c("year", "text")) %>%
  full_join(budget00, by = c("year", "text")) %>%
  full_join(budget01, by = c("year", "text")) %>%
  full_join(budget02, by = c("year", "text")) %>%
  full_join(budget03, by = c("year", "text")) %>%
  full_join(budget04, by = c("year", "text")) %>%
  full_join(budget05, by = c("year", "text")) %>%
  full_join(budget06, by = c("year", "text")) %>%
  full_join(budget07, by = c("year", "text")) %>%
  full_join(budget08, by = c("year", "text")) %>%
  full_join(budget09, by = c("year", "text")) %>%
  full_join(budget10Lab, by = c("year", "text")) %>%
  full_join(budget10, by = c("year", "text")) %>%
  full_join(budget11, by = c("year", "text")) %>%
  full_join(budget12, by = c("year", "text")) %>%
  full_join(budget13, by = c("year", "text")) %>%
  full_join(budget14, by = c("year", "text")) %>%
  full_join(budget15a, by = c("year", "text")) %>%
  full_join(budget15b, by = c("year", "text")) %>%
  full_join(budget16, by = c("year", "text")) %>%
  full_join(budget17a, by = c("year", "text")) %>%
  full_join(budget17b, by = c("year", "text")) %>%
  full_join(budget18, by = c("year", "text")) %>%
  full_join(budget20, by = c("year", "text")) %>%
  full_join(budget21a, by = c("year", "text")) %>%
  full_join(budget21b, by = c("year", "text")) %>%
  full_join(budget22, by = c("year", "text")) %>%
  full_join(budget23, by = c("year", "text"))

c$party <- c("Labour", "Labour", "Labour", "Labour", "Labour", "Labour", "Labour", "Labour" ,"Labour","Labour", "Labour", "Labour", "Labour", "Labour", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative", "Conservative")

c$speaker <- c("Gordon Brown 97","Gordon Brown 98", "Gordon Brown 99", "Gordon Brown 00", "Gordon Brown 01", "Gordon Brown 02", "Gordon Brown 03", "Gordon Brown 04", "Gordon Brown 05", "Gordon Brown 06", "Gordon Brown 07", "Alistair Darling 08",  "Alistair Darling 09", "Alistair Darling March 10", "George Osborne 10","George Osborne 11", "George Osborne 12", "George Osborne 13", "George Osborne 14", "George Osborne March 15", "George Osborne July 15", "George Osborne 16","Phillip Hammond March 17","Phillip Hammond Nov 17","Phillip Hammond 18", "Rishi Sunak 20","Rishi Sunak March 21","Rishi Sunak Oct 21", "Jeremy Hunt 22", "Jeremy Hunt 23")

c$yearInGov <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 1, 2, 3, 1, 2, 3, 4, 5, 6, 6, 1, 1, 1, 2, 2, 3, 4, 1, 2)

#write.csv(c, 'BudgetStatementsCleaned.csv')

#donwload the corpus 
c <- read.csv("~/Documents/ASDS/Thesis /BudgetStatementsCleaned.csv") %>%
  select(-c(X))
```


