---
title: "Word embedidngs using conText"
output: html_document
date: "2023-08-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown contains the code for the word embeding analysis, taking from Rodriguez et al (2023a and 2023b). The analysis used in the thesis uses the wrapper function with 100 boostraps. In this markdown, however, the analysis to complete each embedding once is also included below. 

Rodriguez, P., Spirling, A., and Stewart B. (2023a) _conText: 'a la Carte' on Text (ConText) Embedding Regression_. R package version 1.4.3. Available at: https://CRAN.R-project.org/package=conText 
Rodriguez, P., Spirling, A., and Stewart, B. (2023b) ‘Embedding Regression: Models for Context-Specific Description and Inference’,  American Political Science Review, pp. 1-20. 


```{r}
# other libraries used in this guide
library(quanteda)
library(dplyr)
library(text2vec)
library(conText)
library(tidyverse)
# If there is a problem witht he dfm, run this code: 
#install.packages('Matrix')
#library(Matrix)
```


```{r}
c <- read.csv("~/Documents/ASDS/Thesis /BudgetStatementsCleaned.csv") %>%
  select(-c(X))

corp <- corpus(c)

docnames(corp) <- c$speaker
  #c("Gordon Brown 97","Gordon Brown 98", "Gordon Brown 99", "Gordon Brown 00", "Gordon Brown 01", "Gordon Brown 02", "Gordon Brown 03", "Gordon Brown 04", "Gordon Brown 05", "Gordon Brown 06", "Gordon Brown 07", "Alistair Darling 08",  "Alistair Darling 09", "Alistair Darling March 10", "George Osborne 10","George Osborne 11", "George Osborne 12", "George Osborne 13", "George Osborne 14", "George Osborne March 15", "George Osborne July 15", "George Osborne 16","Phillip Hammond March 17","Phillip Hammond Nov 17","Phillip Hammond 18", "Rishi Sunak 20","Rishi Sunak March 21","Rishi Sunak Oct 21", "Jeremy Hunt 22", "Jeremy Hunt 23")

# Clean corpus 
budget_tokens <- tokens(corp, remove_punct = TRUE, remove_numbers = TRUE , remove_symbols = T, remove_separators = T) %>%
  tokens_remove(c(stopwords("en"), "can", "also", "get", "now", "government", "uk", "make", "already", "means", "next", "us", "mr", "speaker", "deputy", "want", "like", "tax", "year", "per", "cent", "today", "new", "2015-16", "rhf",  "its", "well", "were", "weve", "thats", "march", "cent", "pre-budget", "honourable",  "going", "don’t", "let", ".", "cent", "say", "people", "plan", "today", "largest", "thank", "column", "will", "country", "need", "deliver", "announce", "propose", "promise", "week", "countries", "set", "budget", "billion", "million", "april", "britain", "promis", "invest", "support", "just", "meet", "take", "work", "bn", "economic", "economy", "secretaries", "made", "announcing", "are", "able", "forecast", "united kingdom", "british", "get", "year", "madame", "measure", "done", "take", "fact", "one", "even","making", "many", "still", "without", "know", "course", "way", "much", "almost", "really", "put", "part", "know", "makes", "another", "many", "least", "yet", "back", "getting", "terms", "believe", "long", "good", "must", "look", "continue", "come", "far", "past", "see", "what", "real", "getting", "keep", "enough", "find", "simply", "bill", "comes", "goes", "come", "sure", "taking", "place", "last", "around", "actually", "however", "think", "many", "first", "needs", "right", "less", "little", "bring", "thing", "bring", "across", "needed")) %>% 
  tokens_remove(pattern = "\\d{4}-\\d{2}") %>% tokens_wordstem()

toks_nostop <- tokens_select(budget_tokens, min_nchar=3)

# only use features that appear at least 5 times in the corpus
feats <- dfm(toks_nostop, tolower=T, verbose = FALSE) %>% dfm_trim(min_termfreq = 5) %>% featnames()
toks_nostop_feats <- tokens_select(toks_nostop, feats, padding = TRUE)

# summary(toks_nostop_feats)

```

Now we have to build nine tokenised corpori of contexts (one for each embedding)
```{r}
income_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "incom*", window = 5L)
job_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "job*", window = 5L)
housing_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "hous*", window = 5L)
elderly_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "elder*", window = 5L)
child_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "child*", window = 5L)
parent_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "parent*", window = 5L)
family_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "famil*", window = 5L)
education_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "educat*", window = 5L)
nhs_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "nhs*", window = 5L)
immi_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "immi*", window = 5L)
homeless_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "home*", window = 5L)
invest_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "invest*", window = 5L)
benefit_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "benefit*", window = 5L)
cut_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "cut*", window = 5L)
public_toks <- conText::tokens_context(x = toks_nostop_feats, pattern = "public*", window = 5L)

```

Load in the pre-trained word embeddings and create trasnformation matrix 
```{r}
# Glove pre trained word embeddings with 300 dimensions. 
cr_glove <- readRDS("/Users/ruthboardman/Documents/ASDS/Thesis /cr_glove.rds")



#' # construct feature-co-occurrence matrix
toks_fcm <- fcm(toks_nostop, context = "window", window = 6,
 count = "weighted", weights = 1 / (1:6), tri = FALSE)

# Get transportation matrix 
local_transform <- compute_transform(x = toks_fcm, pre_trained = cr_glove, weighting = 'log')

```

Use the wrapper function to bootsrap the results. The output from this is used in the thesis. 
```{r}
feats_inc <- featnames(dfm(income_toks))
feats_educ <- featnames(dfm(education_toks))

# compare nearest neighbors between groups
set.seed(2021L)
income_party_nns <- get_nns(x = income_toks, N = 15,
        groups = docvars(income_toks, 'party'),
        candidates = feats,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

educ_party_nns <- get_nns(x = education_toks, N = 15,
        groups = docvars(education_toks, 'party'),
        candidates = feats_educ,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_child <- featnames(dfm(child_toks))
child_party_nns <- get_nns(x = child_toks, N = 15,
        groups = docvars(child_toks, 'party'),
        stem = F,
        candidates = feats_child,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_elderly<- featnames(dfm(elderly_toks))
eld_party_nns <- get_nns(x = elderly_toks, N = 15,
        groups = docvars(elderly_toks, 'party'),
        stem = F,
        candidates = feats_elderly,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_family <- featnames(dfm(family_toks))
family_party_nns <- get_nns(x = family_toks, N = 15,
        groups = docvars(family_toks, 'party'),
        stem = F,
        candidates = feats_family,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_parent <- featnames(dfm(parent_toks))
parent_party_nns <- get_nns(x = parent_toks, N = 15,
        groups = docvars(parent_toks, 'party'),
        stem = F,
        candidates = feats_parent,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_invest <- featnames(dfm(invest_toks))
invest_party_nns <- get_nns(x = invest_toks, N = 15,
        groups = docvars(invest_toks, 'party'),
        stem = F,
        candidates = feats_invest,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

feats_job <- featnames(dfm(job_toks))
job_party_nns <- get_nns(x = job_toks, N = 15,
        groups = docvars(job_toks, 'party'),
        stem = F,
        candidates = feats_job,
        pre_trained = cr_glove_subset,
        transform = TRUE,
        transform_matrix = cr_transform,
        bootstrap = TRUE,
        num_bootstraps = 100, 
        confidence_level = 0.95,
        as_list = TRUE)

job_party_nns
invest_party_nns
income_party_nns
educ_party_nns
child_party_nns
eld_party_nns
family_party_nns
parent_party_nns
```

The following code is not included in the thesis, however shows how to complete the embeddings without bootstrapping the results. 
Now build a document feature matrix 
```{r}

income_dfm <- dfm(income_toks, verbose = F)
job_dfm <- dfm(job_toks)
housing_dfm <- dfm(housing_toks)
elderly_dfm <- dfm(elderly_toks)
child_dfm <- dfm(child_toks)
parent_dfm <- dfm(parent_toks)
family_dfm <- dfm(family_toks)
education_dfm <- dfm(education_toks)
nhs_dfm <- dfm(nhs_toks)
immi_dfm <- dfm(immi_toks)
homeless_dfm <- dfm(homeless_toks)
invest_dfm <- dfm(invest_toks)
cut_dfm <- dfm(cut_toks)
public_dfm <- dfm(public_toks)
benefit_dfm <- dfm(benefit_toks)
```

Creat a document embedding matrix for each embedding word. 
```{r}
income_dem <- dem(x = income_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
income_wv_party <- dem_group(income_dem, groups = income_dem@docvars$party)


# job 
job_dem <- dem(x = job_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
job_wv_party <- dem_group(job_dem, groups = job_dem@docvars$party)


#housing 
housing_dem <- dem(x = housing_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
housing_wv_party <- dem_group(housing_dem, groups = housing_dem@docvars$party)


# elderly 
elderly_dem <- dem(x = elderly_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
elderly_wv_party <- dem_group(elderly_dem, groups = elderly_dem@docvars$party)


# child 
child_dem <- dem(x = child_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
child_wv_party <- dem_group(child_dem, groups = child_dem@docvars$party)


# parent 
parent_dem <- dem(x = parent_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
parent_wv_party <- dem_group(parent_dem, groups = parent_dem@docvars$party)


# family 
family_dem <- dem(x = family_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
family_wv_party <- dem_group(family_dem, groups = family_dem@docvars$party)


# education 
education_dem <- dem(x = education_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
education_wv_party <- dem_group(education_dem, groups = education_dem@docvars$party)


# nhs 
nhs_dem <- dem(x = nhs_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
nhs_wv_party <- dem_group(nhs_dem, groups = nhs_dem@docvars$party)


# Immigration
immi_dem <- dem(x = immi_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
immi_wv_party <- dem_group(immi_dem, groups = immi_dem@docvars$party)

# Home
home_dem <- dem(x = homeless_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
home_wv_party <- dem_group(home_dem, groups = home_dem@docvars$party)

#Invest 
invest_dem <- dem(x = invest_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
invest_wv_party <- dem_group(invest_dem, groups = invest_dem@docvars$party)

# Benefit
benefit_dem <- dem(x = benefit_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
benefit_wv_party <- dem_group(benefit_dem, groups = benefit_dem@docvars$party)

# Cut
cut_dem <- dem(x = cut_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
cut_wv_party <- dem_group(cut_dem, groups = cut_dem@docvars$party)

# Public
public_dem <- dem(x = public_dfm, pre_trained = cr_glove, transform = TRUE, transform_matrix = local_transform, verbose = TRUE)
public_wv_party <- dem_group(public_dem, groups = public_dem@docvars$party)

```

Find the nearest ten neighbours for each embedding. 
```{r}
# Nearest neighbour 
income_nns <- nns(income_wv_party, pre_trained = cr_glove, N = 10, candidates = income_wv_party@features, as_list = TRUE)

job_nns <- nns(job_wv_party, pre_trained = cr_glove, N = 10, candidates = job_wv_party@features, as_list = TRUE)

housing_nns <- nns(housing_wv_party, pre_trained = cr_glove, N = 10, candidates = housing_wv_party@features, as_list = TRUE)

elderly_nns <- nns(elderly_wv_party, pre_trained = cr_glove, N = 10, candidates = elderly_wv_party@features, as_list = TRUE)

child_nns <- nns(child_wv_party, pre_trained = cr_glove, N = 10, candidates = child_wv_party@features, as_list = TRUE)

parent_nns <- nns(parent_wv_party, pre_trained = cr_glove, N = 10, candidates = parent_wv_party@features, as_list = TRUE)

family_nns <- nns(family_wv_party, pre_trained = cr_glove, N = 10, candidates = family_wv_party@features, as_list = TRUE)

education_nns <- nns(education_wv_party, pre_trained = cr_glove, N = 10, candidates = education_wv_party@features, as_list = TRUE)

nhs_nns <- nns(nhs_wv_party, pre_trained = cr_glove, N = 10, candidates = nhs_wv_party@features, as_list = TRUE)

immi_nns <- nns(immi_wv_party, pre_trained = cr_glove, N = 10, candidates = immi_wv_party@features, as_list = TRUE)

home_nns <- nns(home_wv_party, pre_trained = cr_glove, N = 10, candidates = home_wv_party@features, as_list = TRUE)

invest_nns <- nns(invest_wv_party, pre_trained = cr_glove, N = 10, candidates = invest_wv_party@features, as_list = TRUE)

benefit_nns <- nns(benefit_wv_party, pre_trained = cr_glove, N = 10, candidates = benefit_wv_party@features, as_list = TRUE)

cut_nns <- nns(cut_wv_party, pre_trained = cr_glove, N = 10, candidates = cut_wv_party@features, as_list = TRUE)

public_nns <- nns(public_wv_party, pre_trained = cr_glove, N = 10, candidates = public_wv_party@features, as_list = TRUE)
```


Find the nearest context neighbours. This gives the whole sentences around the embedding, to help explain the embedding. 
```{r}
f_cont <- ncs(x = family_wv_party, contexts_dem = family_dem, contexts = family_toks, N = 10, as_list = TRUE)
f_cont[["Labour"]]

```


Tranform results intro dataframes and bind the two embeddings together. 
```{r}
# check out results for each party 
inc_l <- as.data.frame(income_nns[["Labour"]]) %>% rename(income = feature)
incl_c <- as.data.frame(income_nns[["Conservative"]]) %>% rename(income = feature)
income <- rbind(inc_l, incl_c)

job_l <- as.data.frame(job_nns[["Labour"]]) %>% rename(job = feature)
job_c <- as.data.frame(job_nns[["Conservative"]]) %>% rename(job = feature)
job <- rbind(job_l, job_c)

hous_l <- as.data.frame(housing_nns[["Labour"]]) %>% rename(house = feature)
hous_c <- as.data.frame(housing_nns[["Conservative"]]) %>% rename(house = feature)
hous <- rbind(hous_c, hous_l)

eld_l <- as.data.frame(elderly_nns[["Labour"]]) %>% rename(elderly = feature)
eld_c <- as.data.frame(elderly_nns[["Conservative"]]) %>% rename(elderly = feature)
eld <- rbind(eld_l, eld_c)

child_l <- as.data.frame(child_nns[["Labour"]]) %>% rename(child = feature)
child_c <- as.data.frame(child_nns[["Conservative"]]) %>% rename(child = feature)
child <- rbind(child_c, child_l)

parent_l <- as.data.frame(parent_nns[["Labour"]]) %>% rename(parent = feature)
parent_c <- as.data.frame(parent_nns[["Conservative"]]) %>% rename(parent = feature)
parent <- rbind(parent_c, parent_l)

fam_l <- as.data.frame(family_nns[["Labour"]]) %>% rename(family = feature)
fam_c <- as.data.frame(family_nns[["Conservative"]]) %>% rename(family = feature)
fam <- rbind(fam_l, fam_c)

educ_l <- as.data.frame(education_nns[["Labour"]]) %>% rename(education = feature)
educ_c <- as.data.frame(education_nns[["Conservative"]]) %>% rename(education = feature)
educ <- rbind(educ_c, educ_l)

nhs_l <- as.data.frame(nhs_nns[["Labour"]]) %>% rename(nhs = feature)
nhs_c <- as.data.frame(nhs_nns[["Conservative"]]) %>% rename(nhs = feature)
nhs <- rbind(nhs_c, nhs_l)

immi_l <- as.data.frame(immi_nns[["Labour"]]) %>% rename(immi = feature)
immi_c <- as.data.frame(immi_nns[["Conservative"]]) %>% rename(immi = feature)
immi <- rbind(immi_l, immi_c)

home_l <- as.data.frame(home_nns[["Labour"]]) %>% rename(home = feature)
home_c <- as.data.frame(home_nns[["Conservative"]]) %>% rename(home = feature)
home <- rbind(home_c, home_l)

invest_l <- as.data.frame(invest_nns[["Labour"]]) %>% rename(invest = feature)
invest_c <- as.data.frame(invest_nns[["Conservative"]]) %>% rename(invest = feature)
invest <- rbind(invest_c, invest_l)

benefit_l <- as.data.frame(benefit_nns[["Labour"]]) %>% rename(benefit = feature) 
benefit_c <- as.data.frame(benefit_nns[["Conservative"]]) %>% rename(benefit = feature)
benefit <- rbind(benefit_c, benefit_l)

cut_l <- as.data.frame(cut_nns[["Labour"]]) %>% rename(cut = feature) 
cut_c <- as.data.frame(cut_nns[["Conservative"]]) %>% rename(cut = feature)
cut <- rbind(cut_c, cut_l)

public_l <- as.data.frame(public_nns[["Labour"]]) %>% rename(public = feature) 
public_c <- as.data.frame(public_nns[["Conservative"]]) %>% rename(public = feature)
public <- rbind(public_c, public_l)


```

Save data into CVs to put into word 
```{r}
write.csv(income, "income.csv", row.names = F)
write.csv(job, "job.csv", row.names = F)
write.csv(hous, "hous.csv", row.names = F)
write.csv(eld, "eld.csv", row.names = F)
write.csv(child, "child.csv", row.names = F)
write.csv(parent, "parent.csv", row.names = F)
write.csv(fam, "fam.csv", row.names = F)
write.csv(educ, "educ.csv", row.names = F)
write.csv(nhs, "nhs.csv", row.names = F)
write.csv(immi, "immi.csv", row.names = F)
write.csv(invest, "invest.csv", row.names = F)
write.csv(benefit, "benefit.csv", row.names = F) 
write.csv(cut, "cut.csv", row.names = F)
write.csv(public, "public.csv", row.names = F)
```





